\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{raleway}
\usepackage[english]{babel}
\usepackage[dvipsnames]{xcolor}
\usepackage[marginal, norule, perpage]{footmisc}

\renewcommand{\thefootnote}{\Roman{footnote}}

\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=MidnightBlue,
  urlcolor=MidnightBlue
}

\title{
  \textbf{The Hero Project}\\
  \large{Product Specifications}
  \linebreak
  \linebreak
  \small{\texttt{01001000\\01000101\\01010010\\01001111}}
}

\author{
  \begin{tabular}{rl}
    \textbf{Team:}
    & \textsc{Djordjevic} Filip\\
    & \textsc{Reichl} Markus \small{\textit{Product Owner}}\\
    & \textsc{Tekin} Abdurrahim\\
    & \textsc{Wellner} Florian\\
    \\
    \textbf{Supervision:}
    & \textsc{Dolezal} Dominik
  \end{tabular}
}

\begin{document}
\begin{titlepage}
  \clearpage
  \maketitle
  \thispagestyle{empty}
  
  \begin{abstract}
    \begin{flushleft}
      The Hero Project is a \textbf{bullethell roguelike multiplayer RPG} providing a very own storytelling and gameplay experience.
     \end{flushleft}
  \end{abstract}
\end{titlepage}

\tableofcontents
\newpage

\section{Introduction}
The Hero Project is a \textbf{bullethell\footnotemark[1] roguelike\footnotemark[2] multiplayer\footnotemark[3] RPG\footnotemark[4]} providing a very own storytelling and gameplay experience.

\footnotetext[1]{A video game sub-genre where the screen is usually covered in bullets.}
\footnotetext[2]{A video game sub-genre which, based on the \href{http://roguebasin.com/roguelike-definition}{Roguebasin Interpretation}, is defined by 
  \begin{itemize}
    \item \textbf{Permanent Failure:} The player is encouraged to take responsibility for the risks he takes.
    \item \textbf{Procedural Environments:} Most of the game world is generated and provides complexity in resources and other elements of the game.
    \item \textbf{Resources:} The player can manage a limited amount of resources.
  \end{itemize}
  The \href{http://roguebasin.com/roguelike-definition}{Roguebasin}, \href{http://roguebasin.com/index.php?title=Berlin_Interpretation}{Berlin} and \href{http://roguetemple.com/roguelike-definition}{Roguetemple} Interpretation may give a more detailed explaination on this subject.
}
\footnotetext[3]{A multiplayer game allows but does not require clients to play together. The Hero Project is not meant to be played online only!}
\footnotetext[4]{A roleplay game is a game in which the player assumes the roles of characters in a fictional setting and takes responsibility for his acting either thorugh literal acting.}

It is highly inspired by previous titles in the roguelike and roleplay game genres, the most noteworthy being \href{https://realmofthemadgod.com}{Realm of the Mad God}, \href{http://www.devolverdigital.com/games/view/titan-souls}{Titan Souls} and \href{http://dodgeroll.com/gungeon/}{Enter the Gungeon}.

While all mentioned games are using a topdown pixelart setting The Hero Project is drawn in a very unique combination of high and low resolutions.

\section{Project Goals}
The main goal of The Hero Project as a school project is to create a solid base for a video game ready for further development.
This base includes all elements listed in the Product Functions and Product Specifications sections.

\newpage

\section{Product Functions}
\subsection{\texttt{/PF10/} Atificial Intelligence}\label{subsec:pf10ai}
Entities\footnote[1]{Every interacting object in the game is referred to as a (game) entity} similar to a character \ref{subsec:pf20character} are controlled by the game and interact with their environment including the player.
\subsection{\texttt{/PF20/} Character}\label{subsec:pf20character}
A single client is able to control at least one characters actions and manage his inventory \ref{subsec:pf41inventory}.
\subsection{\texttt{/PF21/} Movement}\label{susec:pf21movement}
The player is able to control his characters movement using an input of his choice.
\subsection{\texttt{/PF22/} Item Interaction}\label{subsec:pf22iteminteraction}
The player is able to interact with items \ref{subsec:pf40items} in his inventory \ref{subsec:pf41inventory} and use their effects \ref{subsec:pf30effects} using his input or user interface.
\subsection{\texttt{/PF30/} Effects}\label{subsec:pf30effects}
Game Entities can be given effects which allow them to interact with their environment.
They can be activated or enabled or interact permanently.
The most common effect, which is also implemented in the core game, is an attack.
\subsection{\texttt{/PF30/} Items}\label{subsec:pf40items}
Items are the main resource in the game. They can also be given effects \ref{subsec:pf30effects} which can interact with other entities.
\subsection{\texttt{/PF31/} Inventory}\label{subsec:pf41inventory}
An inventory keeps a limited amount of items and is split into baseitems, equipment and the inventory itself.
Storing an item inside the equipment allows the entity owning it to use its effects.

\end{document}
